---
title: "Juvenile energetic trade-offs analysis"
author: "Nic TG"
date: "1/6/2022"
output: 
  github_document:
    toc: true
    html_preview: true

---

### Data Dictionary

#### C-peptide of insulin dataset variables:

<font size = "2">
In `cp_raw` every row is a unique urine sample, which is from a subject sampled on a given date and time.

```{r, include= F, message = F}
load("cp dataset full.Rdata", verbose = T)
names(cp_raw)
```


`group`: chr, social group of juvenile subject  
`subj`: chr, 4 character code of subject  
`date`: Date, date of urine sample collection  
`time`: POSIXlt, time of sample collection  
`sample_number`: int, unique identifier of sample  
`Cr`: num, creatinine value of sample  
`SG`: num, specific gravity of sample, value is SG-1 * 100 (e.g. 1.23 - 1 * 100 = 23)  
`Cr.plate.number`: int, original plate number of creatinine assay  
`Cr.date`: Date, date of creatinine assay  
`cp_dilution`: int, a dilution factor X, i.e. sample ran for cp at 1:X dilution  
`cp_run`: int, group of cp samples put through gamma counter  
`cp_assay_date`: chr, date when cp was read in gamma counter  
`pg.ml_ucp`: num, raw concentration of cp in assayed sample in pg/ml * dilution factor (dilution controlled for in gamma counter input)  
`cp_batch`: int, set of 50 samples used with a given cp ria kit  
`stdcr_CP`: num,  
`stsg_CP`: num, pg.ml_ucp controlling for sample specific gravity, stdsg_CP = pg.ml_ucp * mean(SG)/sample SG  
`cp_note`: chr, any relevant notes about cp value  
`month`: num, month of sample collection  
`year`: num, year of sample collection  

</font>

#### Neopterin dataset variables:

```{r, include= F, message = F}
load("neo dataset full.Rdata", verbose = T)
names(neo_data_full)
```

<font size = "2">
Like `cp_raw`, every row in `neo_data_full` is a unique urine sample, which is from a subject sampled on a given date and time. Many columns in these two datasets are shared.

**Shared columns**:  
`group`: chr, social group of juvenile subject  
`subj`: chr, 4 character code of subject  
`date`: Date, date of urine sample collection
`month`: num, month of urine sample collection
`year`: num, year of urine sample collection
`time`: POSIXlt, time of sample collection  
`sample_number`: int, unique identifier of sample  
`Cr`: num, creatinine value of sample  
`SG`: num, specific gravity of sample, value is SG-1 * 100 (e.g. 1.23 - 1 * 100 = 23)  
**Unique to Neo**:    
`month.name`: factor, 3 letter code for month  
`mum`: factor, 3 letter code for juv's mum, can be optionally used as clustering variable in regression  
`bday`: Date, subject's birthday  
`weaning`: Date, subject's last day observed nursing from mother  
`mid`: Date, the midday of each month, used for calculating monthly ages  
`neo_value`: num, raw value of neopterin assay  
`CV`: num, coefficient of variation of neopterin sample assayed in duplicate  
`neo_plate_number`: num, immuno plate on which final value of sample was assayed  
`neo_dilution`: int, a dilution factor X, sample was diluted 1:X for its final value  
`neo_date_assayed`: Date, assay date of final neo value  
`neo_note`: chr, any relevant note about sample when assayed for neo  
`SG_corr_fac`: num, mean(SG)/sample SG  
`neo_sg`: num, final value of neo to be used for analysis, `neo_sg = neo_value * neo_dilution * SG_corr_fac`  

</font>

#### Behavioral dataset

behav dataset, is a unique subject-month of behavioral observation, and variables. in here are proportion of observed time in a given behavioral activity (giving grooming, playing, etc.)
or number of counts in a given month that a subject gave or received aggression.

### Analysis

#### Background and hypothesis
#### Modeling approach
